A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Update my report bib
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1068 43ef1190-90fd-4dd7-a769-d0121f02b80e
Use colors that flatten fine to grayscale
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1070 43ef1190-90fd-4dd7-a769-d0121f02b80e
Fix the percentage labels
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1071 43ef1190-90fd-4dd7-a769-d0121f02b80e

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days\todo{explain number of occur; fix labels}\todo{qqplot in report}.

@@

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. On the vertical axis, the size of the boxes
    are determined by the fraction of the types of resources. On the
    horizontal axis the width of the boxes is proportional to the
    total counts, using the same bins as in
    Figure~\ref{fig:hardall}. Yellow boxes denote SPARQL endpoints,
    green dataset descriptions, blue generic information resources and
    red vocabularies.}
  \label{fig:hardtable}
\end{figure}

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{egne,webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs,similarity,optimization}

>>>>

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days\todo{explain number of occur}\todo{qqplot in report}.

@@

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. On the vertical axis, the size of the boxes
    are determined by the fraction of the types of resources. On the
    horizontal axis the width of the boxes is proportional to the
    total counts, using the same bins as in
    Figure~\ref{fig:hardall}. From bottom to top, light blue boxes
    denote SPARQL endpoints, dark violet dataset descriptions, orange
    generic information resources and light orange vocabularies.}
  \label{fig:hardtable}
\end{figure}

@@

%\bibliographystyle{plain}
\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{egne,webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs,similarity,optimization}
